### 2013-07-05 cws/emnlp_cws/abstract.tex
a bunch of cleanups and additional writing

\begin{abstract}
There are two dominant approaches to Chinese word segmentation problem: word-based and character-based. They each have their own strengths and weaknesses. 
Word-based approaches are better at capturing longer context dependencies, and achieve higher segmentation consistency, whereas character-based approaches model the internal structures of words and can capture more out-of-vocabulary words. It is an intuitive idea to find methods to combine these approaches. Past efforts in combing word and character-based segmenters involve either training many instances of segmenters and polling their results, or designing complex latent-variable methods that incur heavy computational costs. In this paper, we propose an effective joint decoding method using dual decomposition, which does not require any additional training. Our method is simple and easy to implement, and achieves best reported results on 6 out of 7 standard SIGHAN evaluation datasets.
\end{abstract}

>>>>

\begin{abstract}
There are two dominant approaches to the Chinese word segmentation problem: word-based and character-based models, each with respective strengths and weaknesses. Prior work has shown that gains in segmentation performance can be achieved from combining these two types of models; however, past efforts involve either training many instances of segmenters and polling their results, or designing complex latent-variable methods that incur heavy computational costs. In this paper, we propose an effective and consistent joint decoding method using dual decomposition, which does not require any additional training. Our method is simple and easy to implement, and achieves the best reported results to date on 6 out of 7 standard SIGHAN evaluation datasets.
\end{abstract}

%%
%Word-based approaches are better at capturing longer context dependencies, and achieve higher segmentation consistency, whereas character-based approaches model the internal structures of words and can capture more out-of-vocabulary words. It is an intuitive idea to find methods to combine these approaches.

### 2013-07-05 cws/emnlp_cws/conclusion.tex
a bunch of cleanups and additional writing

In this paper we presented ... blah blah.
Stress the simplicity and effectiveness of our method.

>>>>

In this paper we presented an approach to Chinese word segmentation using dual decomposition for system combination. We demonstrated that this method allows for joint decoding of existing CWS systems that performs better than either system alone, and further achieves the best performance reported to date on standard datasets for the task.

We also demonstrated that our joint system produces more consistent segmentations than our baselines. This property that has potentially important downstream impacts for many Chinese NLP tasks, though it remains to test this empirically.

Perhaps most importantly, our approach is straightforward to implement and does not require retraining of the underlying segmentation models used. This suggests its potential for broader applicability in real-world settings than existing approaches to combining character-based and word-based models for Chinese word segmentation.

### 2013-07-05 cws/emnlp_cws/discussion.tex
a bunch of cleanups and additional writing

@@

\cite{Chang:2008:ACL} have shown that increased segmentation consistency is correlated with better machine translation performance. Following their method for calculating the conditional entropy of a segmentation system, we see in Table [insert table] that our dual decomposition method achieves the most consistent results on 6 out of 7 datasets.

@@

as crf
0.0635314146511
as pct
0.0603263902622
as dd
0.055097582491
cityu crf
0.0649537861096
cityu pct
0.0730776631941
cityu dd
0.0618197636595
msr crf
0.073782773985
msr pct
0.0628241148726
msr dd
0.054883418641
pku crf
0.0888607888366
pku pct
0.0996634383663
pku dd
0.086635535204

\subsection{Oracle}

Following \cite{Sun:2010:COLING}, we run an oracle experiment to estimate the upper bound of improvement possible via system combination to further contextualize our results.

To do so, we combine our two baselines with the gold-standard segmentation. Each character in the test set is labeled with three \emph{B} or \emph{I} tags, \emph{B} when it begins a word and \emph{I} when it is word-medial or word-final, according to our two baselines and the gold standard. We then create oracle labels by majority vote: if the baselines agree, their label is used; if they disagree, the gold label is used.

The results of this oracle experiment, shown in Table [insert table], show that [what do they show? DD approaches the upper bound possible?]

% this is here to know what each column means in the output below
%=== TOTAL INSERTIONS:	75
%=== TOTAL DELETIONS:	84
%=== TOTAL SUBSTITUTIONS:	783
%=== TOTAL NCHANGE:	942
%=== TOTAL TRUE WORD COUNT:	11989
%=== TOTAL TEST WORD COUNT:	11980
%=== TOTAL TRUE WORDS RECALL:	0.928
%=== TOTAL TEST WORDS PRECISION:	0.928
%=== F MEASURE:	0.928
%=== OOV Rate:	0.022
%=== OOV Recall Rate:	0.810
%=== IV Recall Rate:	0.930
Scoring Oracle Output, Sighan 2003
for as
	sighan2003/as.oracle	75	84	783	942	11989	11980	0.928	0.928	0.928	0.022	0.810	0.930
for cityu
	sighan2003/cityu.oracle	402	333	2364	3099	35087	35156	0.923	0.921	0.922	0.071	0.824	0.931
for ctb
	sighan2003/ctb.oracle	920	1005	4490	6415	39921	39836	0.862	0.864	0.863	0.181	0.773	0.882
for pku
	sighan2003/pku.oracle	186	187	1593	1966	17194	17193	0.896	0.897	0.897	0.069	0.834	0.901

Scoring Oracle Output, Sighan 2005
for as
	sighan2005/as.oracle	1855	726	9980	12561	122610	123739	0.913	0.904	0.908	0.043	0.722	0.921
for cityu
	sighan2005/cityu.oracle	577	371	3038	3986	40936	41142	0.917	0.912	0.914	0.074	0.817	0.925
for msr // currently broken
	sighan2005/msr.oracle	81	107	1066	1254	10987	10961	0.893	0.895	0.894	0.025	0.584	0.901
for pku
	sighan2005/pku.oracle	800	1661	9646	12107	104372	103511	0.892	0.899	0.895	0.058	0.815	0.896

\subsection{Error analysis}
% this makes sense, i will do this tomorrow
Maybe look at cases where the model choose the worse of the two instead of the better of the two. See if there are patterns or insights we can draw. Not very important for a short paper.

some errors where DD picks the wrong model:
gold: 有 亭台樓閣 流水
CRF: 亭台 樓閣  <-- DD
PCT: 亭台樓閣

gold: 大規模 海陸空 聯合 軍演   
CRF: 大規模 海 陸空 聯合 軍演   <-- DD
PCT: 大規模 海陸空 聯合 軍演

gold: 在 李鄭屋邨 附近
CRF: 在 李鄭屋邨 附近
PCT: 在 李鄭屋 邨 附近   <-- DD

gold: 麥 父 笑說
CRF:  麥 父 笑說
PCT: 麥父 笑說    <-- DD

gold: 天氣 熱 時 冷氣 大 開     
CRF: 天氣 熱 時 冷氣 大 開     
PCT: 天氣 熱時 冷氣 大 開     <-- DD

>>>>

On the whole, dual decomposition produces state-of-the-art segmentations that are more accurate, more consistent, and more successful at inducing out-of-vocabulary words than the baseline systems that it combines.

@@

\cite{Chang:2008:ACL} have shown that increased segmentation consistency is correlated with better machine translation performance. Following their method for calculating the conditional entropy of a segmentation system, we see in Table [insert table] that our dual decomposition method achieves the most consistent segmentations (lowest conditional entropy) on 6 out of 7 datasets.

@@

as crf
0.0635314146511
as pct
0.0603263902622
as dd
0.055097582491
cityu crf
0.0649537861096
cityu pct
0.0730776631941
cityu dd
0.0618197636595
msr crf
0.073782773985
msr pct
0.0628241148726
msr dd
0.054883418641
pku crf
0.0888607888366
pku pct
0.0996634383663
pku dd
0.086635535204
%
%\subsection{Oracle}
%
%Following \cite{Sun:2010:COLING}, we run an oracle experiment to estimate the upper bound of improvement possible via system combination to further contextualize our results. 
%
%To do so, we combine our two baselines with the gold-standard segmentation. Each character in the test set is labeled with three \emph{B} or \emph{I} tags, \emph{B} when it begins a word and \emph{I} when it is word-medial or word-final, according to our two baselines and the gold standard. We then create oracle labels by majority vote: if the baselines agree, their label is used; if they disagree, the gold label is used.
%
%The results of this oracle experiment, shown in Table [insert table], show that [what do they show? DD approaches the upper bound possible?]
%
%% this is here to know what each column means in the output below
%%=== TOTAL INSERTIONS:	75
%%=== TOTAL DELETIONS:	84
%%=== TOTAL SUBSTITUTIONS:	783
%%=== TOTAL NCHANGE:	942
%%=== TOTAL TRUE WORD COUNT:	11989
%%=== TOTAL TEST WORD COUNT:	11980
%%=== TOTAL TRUE WORDS RECALL:	0.928
%%=== TOTAL TEST WORDS PRECISION:	0.928
%%=== F MEASURE:	0.928
%%=== OOV Rate:	0.022
%%=== OOV Recall Rate:	0.810
%%=== IV Recall Rate:	0.930
%Scoring Oracle Output, Sighan 2003
%for as
%	sighan2003/as.oracle	79	88	173	340	11989	11980	0.978	0.979	0.979	0.071	0.940	0.981
%for cityu
%	sighan2003/cityu.oracle	402	333	893	1628	35087	35156	0.965	0.963	0.964	0.073	0.823	0.976
%for ctb
%	sighan2003/ctb.oracle	929	1014	2504	4447	39921	39836	0.912	0.914	0.913	0.230	0.822	0.939
%for pku
%	sighan2003/pku.oracle	189	190	392	771	17194	17193	0.966	0.966	0.966	0.138	0.925	0.973
%Scoring Oracle Output, Sighan 2003
%for as
%	sighan2005/as.oracle	1876	748	2542	5166	122610	123739	0.973	0.964	0.969	0.099	0.890	0.982
%for cityu
%	sighan2005/cityu.oracle	577	371	1136	2084	40936	41142	0.963	0.958	0.961	0.075	0.839	0.973
%for msr // currently broken
%	sighan2005/msr.oracle	81	107	165	353	10987	10961	0.975	0.978	0.976	0.065	0.934	0.978
%for pku
%	sighan2005/pku.oracle	803	1664	2505	4972	104372	103511	0.960	0.968	0.964	0.124	0.924	0.965
%

\subsection{Error analysis}

Since dual decomposition is a method of joint decoding, it is liable to reproduce errors made by the constituent systems. In the example below, dual decomposition output follows the incorrect segmentation of the character-based CRF in oversegmenting the compound "sea, land, and air."

%some errors where DD picks the wrong model:
%gold: 有 亭台樓閣 流水
%CRF: 亭台 樓閣  <-- DD
%PCT: 亭台樓閣
\begin{tabbing}

\ \ \ \ \= \emph{English}\ \ \ \ \= Large-scale sea, land, and air \\ 
\> \> joint military exercises\\
\> \emph{Gold}\> 大规模 / 海陆空 / 联合 / 军演\\

\> \emph{CRF}\> 大规模 / 海 / 陆空 / 联合 / 军演\\

\> \emph{PCPT}\> 大规模 / 海陆空 / 联合 / 军演\\

\> \emph{DD}\> 大规模 / 海 / 陆空 / 联合 / 军演\\
\end{tabbing}

Nevertheless, in many cases the relative confidence of each model means that dual decomposition is capable of using information from both sources to generate a series of correct segmentations better than either baseline model alone. The example below shows a difficult-to-segment proper name comprised of common characters, which results in undersegmentation by the character-based CRF and oversegmentation by the word-based Perceptron, but our method achieves the correct middle ground.

\begin{tabbing}
\ \ \ \ \= \emph{English}\ \ \ \ \= Tian Yage's creations \\
\> \emph{Gold} \>   田雅各 / 的 / 创作 \\
\> \emph{CRF} \>  田雅各的 / 创作 \\
\> \emph{PCPT} \>  田雅 / 各 / 的 / 创作 \\
\> \emph{DD} \>  田雅各 / 的 / 创作 \\
\end{tabbing}

A powerful feature of the dual decomposition approach is that it can generate correct segmentation decisions in cases where a voting or polling-of-experts model could not, since joint decoding allows the sharing of information at decoding time. In the following example, both baseline models miss the contextually clear grammatical role of 上 (``above") and instead produce the otherwise common compound 上去 (``go up"); dual decomposition allows the model to generate the correct segmentation.

\begin{tabbing}
\ \ \ \ \= \emph{English}\ \ \ \ \= Enjoy a bit of snack food, ... \\
\> \emph{Gold} \>  享受 / 一点 / 点心 /  ，\\
\> \emph{CRF} \> 享受 / 一点点 / 心 / ，\\
\> \emph{PCPT} \> 享受 / 一点点 / 心 / ， \\
\> \emph{DD} \>  享受 / 一点 / 点心 / ，\\
\end{tabbing}
We found more than 400 such surprisingly accurate instances in our dual decomposition output.
%
%gold: 在 李鄭屋邨 附近
%CRF: 在 李鄭屋邨 附近
%PCT: 在 李鄭屋 邨 附近   <-- DD
%
%gold: 麥 父 笑說
%CRF:  麥 父 笑說
%PCT: 麥父 笑說    <-- DD
%
%gold: 天氣 熱 時 冷氣 大 開     
%CRF: 天氣 熱 時 冷氣 大 開     
%PCT: 天氣 熱時 冷氣 大 開     <-- DD

### 2013-07-05 cws/emnlp_cws/experiment.tex
a bunch of cleanups and additional writing

\subsection{Datasets}
Our test data is the standard SIGHAN 2003 \cite{Sproat:2003:SIGHAN} and 2005 \cite{Emerson:2005:SIGHAN} bake-off datasets. [Add a note here about why not using CTB - who figured out it was broken, how do we know not to use it?]

>>>>

\subsection{Datasets}
We run our experiments on the SIGHAN 2003 \cite{Sproat:2003:SIGHAN} and 2005 \cite{Emerson:2005:SIGHAN} bake-off datasets. Specifically, we use the standard training and test splits for the 2003 Academia Sinica (AS), Peking University (PU), and City University of Hong Kong (CU) datasets as well as the 2005 AS, PU, CU, and Microsoft Research (MSR) datasets. We do not use the 2003 Chinese Treebank dataset because... [why exactly?]
